{ \renewcommand{\leftmark}{ACKNOWLEDGEMENTS}
\section*{Acknowledgements}\addcontentsline{toc}{chapter}{Acknowledgements}
%Main supervisor: Prof. Dr. Volker Sieber
%Second supervisor: Dr. Jochen Schmid
%Other academic staff in your department: Marius Rütering, Nina Rimmel, Daniel Bauer, Irina Funk, Sumanth Ranganathan, André Pick, Jörg Carsten, Jose Guillermo Ortiz Tena, Broder Rühmann, Michael Loscar, 
%Technical or support staff in your department: Thomas Howe, Irmgard Urban, Elisabeth Aichner, Karola Wiesmüller, Alfiya Wohn, Petra Lommes
%Academic staff from other departments: Matthias Petzold, Franziska Elchlepp, Mareike Wenning, Christopher Huptas
%Other institutions, organizations or companies: Everybody I did not mention, but would have liked to be mentioned. Portugal (especially Christophe Roca, Silvia Antunes)/Japan (especially Shosuke Ypshida, Mitsuhiro Kanoh, Wataru Shinohara). Software Carpentry (especially Greg Wilson). Bayerisches Staatsministerium für Wirtschaft, Infrastruktur, Verkehr und Technologie
%Family *
%Friends *: Fox
%
%I would like to express my very great appreciation to ***
%I would like to offer my special thanks to ***
%Advice given by *** has been a great help in ***
%I am particularly grateful for the assistance given by ***
%Assistance provided by *** was greatly appreciated.
%I wish to acknowledge the help provided by ***
%Dr *** provided me with very valuable ***
%I would like to thank the following companies for their assistance with the collection of my data:
%         ***
%         ***
%My special thanks are extended to the staff of *** company for ***
%https://elc.polyu.edu.hk/fyp/html/ack.htm
%
%
%
Doctoral theses are rarely the product of the sole efforts of only one person. This is true for this work as well. It would not have been possible without the support of others.

First and foremost, I would like to express my deep gratitude towards \textit{Professor Volker Sieber} for giving me the chance to work on this seminal topic. I would like to offer my special thanks to \textit{Jochen Schmid} for his guidance and helpful discussions.

For their invaluable help during the fermentations of \rolf{} and \comm{}, I especially thank \textit{Thomas Howe}, \textit{Nina Rimmel}, \textit{Marius Rütering}, \textit{Jochen Schmid} and \textit{Irmgard Urban}. The fruitful discussions with and the pleasant working atmosphere created by 
\textit{Elisabeth Aichner}, 
\textit{Daniel Bauer}, 
\textit{Jörg Carsten}, 
\textit{Irina Funk}, 
\textit{Petra Lommes}, 
\textit{Michael Loscar}, 
\textit{Ulrike Obst}, 
\textit{Jose Guillermo Ortiz Tena}, 
\textit{André Pick}, 
\textit{Sumanth Ranganathan}, 
\textit{Nina Rimmel}, 
\textit{Broder Rühmann}, 
\textit{Marius Rütering}, 
\textit{Jochen Schmid}, 
\textit{Irmgard Urban}, 
\textit{Karola Wiesmüller} and
\textit{Alfiya Wohn}
are appreciated. 

\nomenclature[latabbr_TUM]{TUM}{Technische Universität München}
\nomenclature[latabbr_3D]{3D}{three-dimensional}
\nomenclature[latabbr_IGB]{IGB}{Institut für Grenzflächen- und Bioverfahrenstechnik}
I am particularly grateful for the assistance given by \textit{Franziska Elchlepp} (TUM Library Straubing), \textit{Matthias Petzold} (3D-printing at Biogenic Polymers), \textit{Melanie Speck} and \textit{Harald Strittmatter} (Bio, Electro and Chemocatalysis BioCat, Fraunhofer IGB), \textit{Mitsuhiro Kanoh}, \textit{Wataru Shinohara} and \textit{Shosuke Yoshida} (all three Keio University, Japan) and \textit{Silvia Antunes} and \textit{Christophe Roca} (both Universidade Nova de Lisboa, Portugal). For proofreading the thesis and parts thereof at its different stages my sincerest thanks go to \textit{Sumanth Ranganathan}. For teaching me how to make better use of modern software development tools in research and how to teach them I would like to thank \textit{Software Carpentry} and especially its founder, \textit{Greg Wilson}. 

I would also like to thank everybody I did not mention, but who would have liked to be mentioned. I wish to thank my family for support and encouragement throughout the years. Finally, I wish to thank my reliable friend \textit{Fox} for executing my commands and performing calculations for this thesis. You probably had to work hardest for this thesis.

\nomenclature[latabbr_FLOSS]{FLOSS}{free/libre open-source software}
Special thanks goes to everybody out there contributing to \textit{free/libre and open-source software} (FLOSS). This thesis would not have been possible without.
