	{Acetic acid} & {\SIpct{100}, Ph. Eur., extra pure} & {CRG} \\
	{Acetonitrile} & {≥\SIpct{99.9}, Reag. Ph. Eur.} & {VWR} \\
	{Agar-agar} & {for microbiology} & {CRG} \\
	{Agencourt AMPure XP} & {-} & {BCG} \\
	{Ammonia} & {\SIrange{30}{33}{\percent}, extra pure} & {CRG} \\
	{Ammonium chloride} & {-} & {MBB} \\
	{Aniline blue} & {certified by the Biological Stain Commission, dye content: \SIpct{65}} & {SAC} \\
	{Antifoam B} & {-} & {APM} \\
	{\textsc{l}-(−)-Arabinose} & {≥\SIpct{99}} & {EMD} \\
	{2,2$'$-Azino-bis(3-ethylbenzothiazoline-6-sulphonic acid) diammonium salt} & {≥\SIpct{98}} & {SAC} \\
	{Boric acid} & {for electrophoresis, ≥\SIpct{99.5}} & {SAC} \\
	{Bovine serum albumin} & {≥\SIpct{96}} & {SAC} \\
	{Calcium chloride dihydrate} & {≥\SIpct{99}, p.a., ACS} & {CRG} \\
	{Calcium chloride dihydrate} & {ACS, Reag. Ph Eur} & {MK} \\
	{Calibration buffer pH 10} & {\num[separate-uncertainty=true]{10.00(2)}} & {VWR} \\
	{Calibration buffer pH 4} & {\num[separate-uncertainty=true]{4.00(2)}} & {VWR} \\
	{Calibration buffer pH 7} & {\num[separate-uncertainty=true]{7.00(2)}} & {VWR} \\
	{Casein peptone} & {pancreatic digest, for microbiology} & {CRG} \\
	{Chloroform/Isoamyl alcohol (24:1)} & {for extraction of nucleic acids} & {CRG} \\
	{Citric acid} & {≥\SIpct{99.5}, p.a., ACS} & {CRG} \\
	{Cobalt chloride hexahydrate} & {\SIpct{98}} & {AAG} \\
	{Copper sulphate pentahydrate} & {≥\SIpct{99.0}} & {SAC} \\
	{Dimethylsulphoxide} & {≥\SIpct{99.8}, p.a.} & {CRG} \\
	{Dimethylsulphoxide} & {≥\SIpct{99.5}} & {KSF} \\
	{dNTP mix} & {\SImM{10}} & {RLD} \\
	{Ethidium bromide} & {\SIgpl{10}} & {CRG} \\
	{Ethylenediaminetetraacetic acid} & {≥\SIpct{99}, p.a., ACS} & {CRG} \\
	{Ferric sulphate heptahydrate} & {ACS reagent, reag. ISO, reag. Ph. Eur., ≥\SIpct{99.0}} & {SAC} \\
	{Formic acid} & {≥\SIpct{98.0}, p. a.} & {ACG} \\
	{Formic acid} & {~\SIpct{98}} & {SAC} \\
	{Fumaric acid} & {≥\SIpct{99.5}, for biochemistry} & {CRG} \\
	{Furfural} & {ACS, ≥\SIpct{98.0}} & {MK} \\
	{\textsc{d}-(+)-Galactosamine hydrochloride} & {≥\SIpct{98}, for biochemistry} & {CRG} \\
	{\textsc{d}-(+)-Glucosamine hydrochloride} & {≥\SIpct{99}} & {EMD} \\
	{\textsc{d}-(+)-Glucose monohydrate} & {for microbiology} & {CRG} \\
	{\textsc{d}-(+)-Glucose monohydrate} & {Ph. Eur.} & {SEG} \\
	{Glycine} & {USP, Ph. Eur., ≥\SIpct{98.5}} & {SEG} \\
	{HF Buffer} & {-} & {NEB} \\
	{Hydrochloric acid} & {\SIM{2}} & {CRG} \\
	{5-(Hydroxymethyl)furfural} & {\SIpct{97}} & {AAG} \\
	{Itaconic acid} & {-} & {ACG} \\
	{Lithium nitrate} & {\SIpct{99}} & {AAG} \\
	{Magnesium sulphate heptahydrate} & {ACS, Reag. Ph Eur, ≥\SIpct{99.5}} & {MK} \\
	{Magnesium sulphate heptahydrate} & {ACS, Reag. Ph. Eur., ≥\SIpct{99.5}} & {MK} \\
	{Malic acid} & {≥\SIpct{99.0}} & {ACG} \\
	{Manganese chloride dihydrate} & {≥\SIpct{99.0}} & {MK} \\
	{Methanol} & {≥\SIpct{99.9}} & {VWR} \\
	{3-Methyl-1-phenyl-2-pyrazoline-5-one} & {\SIpct{99}} & {SAC} \\
	{3-(\textit{N}-Morpholino) propane sulphonic acid} & {≥\SIpct{99.5}} & {CRG} \\
	{Oxalic acid} & {≥\SIpct{99.0}} & {SAC} \\
	{Phenol} & {for extraction of nucleic acids} & {CRG} \\
	{5x Phusion HF Reaction Buffer} & {-} & {NEB} \\
	{Potassium chloride} & {≥\SIpct{99.5}, p.a., ACS, ISO} & {CRG} \\
	{Potassium dihydrogen phosphate} & {≥\SIpct{99}, p.a., ACS} & {CRG} \\
	{Pullulan (\SID{342})} & {analytical} & {PSS} \\
	{Pullulan (\SIkD{1})} & {analytical} & {PSS} \\
	{Pullulan (\SIkD{5})} & {analytical} & {PSS} \\
	{Pullulan (\SIkD{10})} & {analytical} & {PSS} \\
	{Pullulan (\SIkD{20})} & {analytical} & {PSS} \\
	{Pullulan (\SIkD{50})} & {analytical} & {PSS} \\
	{Pullulan (\SIkD{110})} & {analytical} & {PSS} \\
	{Pullulan (\SIkD{200})} & {analytical} & {PSS} \\
	{Pullulan (\SIkD{400})} & {analytical} & {PSS} \\
	{Pullulan (\SIkD{800})} & {analytical} & {PSS} \\
	{Pullulan (\SIMD{1.3})} & {analytical} & {PSS} \\
	{Pullulan (\SIMD{2.5})} & {analytical} & {PSS} \\
	{α-\textsc{l}-(+)-Rhamnose hydrate} & {for microbiology, ≥\SIpct{99.0}} & {SAC} \\
	{RPMI 1640 Vitamins solution (\SI{100}{\concfac})} & {suitable for cell culture} & {SAC} \\
	{Scleroglucan Cs 11} & {-} & {CFS} \\
	{Sodium acetate} & {≥\SIpct{99.5}, p.a., ACS, ISO} & {CRG} \\
	{Sodium chloride} & {-} & {ACG} \\
	{Sodium chloride} & {≥\SIpct{99}, Ph. Eur., USP} & {CRG} \\
	{Sodium dodecyl sulphate} & {≥\SIpct{99}, research grade} & {SEG} \\
	{Sodium glyoxylate monohydrate} & {≥\SIpct{93}} & {SAC} \\
	{Sodium hydroxide} & {≥\SIpct{99}, p.a., ISO} & {CRG} \\
	{Sodium molybdate} & {≥\SIpct{99.5}, p.a.} & {CRG} \\
	{Sodium periodate} & {≥\SIpct{99.8}, ACS} & {SAC} \\
	{Sodium succinate hexahydrate} & {≥\SIpct{99.0}} & {SAC} \\
	{Sodium tartrate} & {≥\SIpct{99}, extra pure} & {CRG} \\
	{Sulphuric acid} & {\SIpct{96}, p.a., ISO} & {CRG} \\
	{Sulphuric acid} & {\SIM{1}} & {CRG} \\
	{TRIS} & {≥\SIpct{99.3}, Buffer Grade} & {CRG} \\
	{TRIS hydrochloride} & {≥\SIpct{99}, p.a.} & {CRG} \\
	{Vanillin} & {\SIpct{99}} & {SAC} \\
	{\textsc{d}-(+)-Xylose} & {≥\SIpct{98.5}, for biochemistry} & {CRG} \\
	{\textsc{d}-(+)-Xylose} & {for biotechnological purposes, ≥\SIpct{98.0} (sum of enantiomers, HPLC) } & {SAC} \\
	{Yeast extract} & {for bacteriology} & {CRG} \\
	{Zinc chloride} & {ACS, ISO, Reag. Ph. Eur., ≥\SIpct{98.0}} & {MK} \\
