	AAG & Alfa Aesar GmbH + Co. KG, Karlsruhe \\
	ACG & AppliChem GmbH, Darmstadt \\
	AHT & Andreas Hettich GmbH \& Co. KG, Tuttlingen \\
	AHW & A. Hartenstein GmbH, Würzburg \\
	AJA & Analytik Jena AG, Jena \\
	APG & Anton Paar GmbH, Graz, Austria \\
	APM & Avantor Performance Materials B.V., Deventer, Netherlands \\
	AT & Agilent Technologies, Waldbronn \\
	BBM & B. Braun Melsungen AG, Melsungen \\
	BCG & Beckman Coulter GmbH, Krefeld \\
	BDG & Bruker Daltonik GmbH, Bremen \\
	BG & BINDER GmbH, Tuttlingen \\
	BGK & BRAND GmbH + Co. KG, Wertheim \\
	BGS & BlueSens gas sensor GmbH, Herten \\
	BIC & Brookhaven Instruments Corporation, Holtsville, NY, USA \\
	BRL & Bio-Rad Laboratories GmbH, Munich \\
	BS & Boekel Scientific, Feasterville, PA, USA \\
	CFS & Cargill France SAS, Saint-Germain-en-Lage, France \\
	CRG & Carl Roth GmbH + Co. KG, Karlsruhe \\
	CZM & Carl Zeiss Microscopy GmbH, Jena \\
	DC & Dionex Corporation, Sunnyvale, CA, USA \\
	DG & DASGIP GmbH, Jülich \\
	DI & Denver Instrument, Bohemia, NY, USA \\
	DMG & Deutsche METROHM GmbH \& Co. KG, Filderstadt \\
	DWO & Dispomed Witt oHG, Gelnhausen \\
	EA & Eppendorf AG, Hamburg \\
	EBG & Edmund Bühler GmbH, Hechingen \\
	ELW & ELGA Lab Water, Celle \\
	EMD & EMD Biosciences, Inc., La Jolla, CA, USA \\
	GBO & Greiner Bio-One GmbH, Frickenhausen \\
	GFL & GFL Gesellschaft für Labortechnik mbH, Burgwedel \\
	GHE & GE Healthcare Europe GmbH, Freiburg \\
	GHU & GE Healthcare UK Ltd., Buckinghamshire, United Kingdom \\
	HA & Harvard Apparatus, Holliston, MA, USA \\
	HBA & Hamilton Bonaduz AG, Bonaduz, Switzerland \\
	HG & Hellma GmbH \& Co. KG, Müllheim \\
	HIG & Heidolph Instruments GmbH \& Co. KG, Schwabach \\
	HPM & HP Medizintechnik GmbH, Oberschleißheim \\
	HSW & Henke-Sass, Wolf GmbH, Tuttlingen \\
	IA & Infors AG, Bottmingen/Basel, Switzerland \\
	ICZ & Ingenieurbüro CAT, M. Zipperer GmbH, Staufen \\
	IFM & ifm electronic, Essen \\
	IG & Implen GmbH, München \\
	IIG & Intas-Science-Imaging Instruments GmbH, Göttingen \\
	IKA & IKA-Werke GmbH \& Co. KG, Staufen \\
	KMG & Spencer Kimball, Peter Mattis and the GIMP Development Team \\
	KSF & Dr. Klaus Schopp Forschung + Technik, Karlsruhe \\
	KSG & KERN \& SOHN GmbH, Balingen \\
	LH & Liebherr Hausgeräte, Ochsenhausen \\
	MBB & Mallinckrodt Baker B. V., Deventer, Netherlands \\
	MCG & Martin Christ Gefriertrocknungsanlagen GmbH, Osterode am Harz \\
	MDG & Motic Deutschland GmbH, Wetzlar \\
	MG & Memmert GmbH + Co. KG, Schwabach \\
	MK & Merck KGaA, Darmstadt \\
	MNG & Macherey-Nagel GmbH \& Co. KG, Düren \\
	MTG & Mettler-Toledo GmbH, Gießen \\
	NEB & New England Biolabs GmbH, Frankfurt am Main \\
	OC & Ohaus Corp., Pine Brook, NJ, USA \\
	PC & Pall Corporation, Ann Arbor, MI, USA \\
	PHK & Peter Huber Kältemaschinenbau GmbH, Offenburg \\
	PL & Phenomenex Ltd., Aschaffenburg \\
	PSS & PSS Polymer Standards Service GmbH, Mainz \\
	QGD & QIAGEN GmbH Deutschland, Hilden \\
	RLD & Rapidozym Gesellschaft für Laborhandel und DNA Diagnostika mbH, Berlin \\
	SAC & Sigma-Aldrich Chemie GmbH, Steinheim \\
	SAG & Sartorius AG, Göttingen \\
	SAK & Sarstedt AG \& Co. KG, Nümbrecht \\
	SBE & SensoQuest Biomedizinische Elektronik GmbH, Göttingen \\
	SDK & Showa Denko K.K., Kawasaki, Japan \\
	SEG & Serva Electrophoresis GmbH, Heidelberg \\
	SIA & SI Analytics GmbH, Mainz \\
	SKK & Shimadzu, Kyoto, Japan \\
	SLI & Sartorius Lab Instruments GmbH \& Co. KG, Göttingen \\
	SSB & Sartorius Stedim Biotech GmbH, Göttingen \\
	SSS & Sartorius Stedim Systems, Göttingen \\
	TBG & Tosoh Bioscience GmbH, Stuttgart \\
	TEL & Thermo Electron LED GmbH, Langenselbold \\
	TFS & Thermo Fisher Scientific Inc., Waltham, MA, USA \\
	UNK & ? \\
	VAG & VACUUBRAND GmbH + Co. KG, Wertheim \\
	VWR & VWR International bvba/sprl, Leuven, Belgium \\
	ZLG & Zefa-Laborservice GmbH, Harthausen \\
