\subsection{Determination of Polymer Mass}
Polymer mass was determined by gravimetry. The empty mass of a pre-dried tube was measured on an appropriate balance: for samples in the single \si{\micro\gram} region, a micro balance (MSE3.6P-000DM, SLI) was used and for samples of several tens of \si{\micro\gram} to single \si{\gram}, an analytical balance (PA214C, OC) was used.

The exopolysaccharide precipitate was collected and air-dried under a fume hood for up to \SImin{30}. In case of small scale precipitations (less than \SIml{50}), the precipitate was transferred into pre-weighed \SIml{1.5} tubes by adding a small amount of precipitant, resuspending the precipitate in it and transferring the precipitate and precipitant with cut \SIml{1.0} tips and a pipette. The tube was centrifuged for \SIs{60} at \SIG{12000} and room temperature. % Source: SK2, p. 110
The supernatant was removed carefully and the precipitate dried to constant mass.

At larger scales, the precipitate was collected from the stirrer or by letting the precipitate settle for at least one day, decanting the supernatant and collecting the precipitate in \SIml{50} tubes. The precipitate was let to settle for at least one day; the supernatant decanted and the precipitate collected in pre-weighed \SIml{1.5} tubes. If necessary, the \SIml{50} tubes were rinsed with precipitant and the remaining precipitate resuspended and transferred into pre-weighed \SIml{1.5} tubes. The tube was centrifuged for \SIs{60} at \SIG{12000} and room temperature. % Source: SK2, p. 110
The supernatant was removed carefully and the precipitate dried to constant mass.

The precipitate was either dried by vacuum drying at \SIdC{60} (VDL 53, BG), % Source: ?
freeze-drying at \SIdC{-40} (Alpha 2-4 LDplus, MCG) or % Source: ?
drying at \SIdC{60} in a heating cabinet (Function Line T12, TFS). % Source: SK2, p. 119

